%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.1 (February 24, 2025)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{enumitem}


%----------------------------------------------------------------------------------------

\begin{document}

	%----------------------------------------------------------------------------------------
	%	TITLE AND CONTACT INFORMATION
	%----------------------------------------------------------------------------------------

	\begin{minipage}[t]{0.45\textwidth}
		\vspace{-\baselineskip}

		\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Alexander}}}}}

		\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Arrico}}}}}

		\vspace{6pt}

		{\huge Software Engineering Manager}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.27\textwidth} % Center column with icons
		\vspace{-\baselineskip}

		\icon{MapMarker}{12}{Brunswick, GA}\\
		\icon{Phone}{12}{(310) 740-5037}\\
		\icon{At}{12}{\href{mailto:alex@arrico.me}{alex@arrico.me}}\\
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.27\textwidth} % Right column with icons
		\vspace{-\baselineskip}

		\icon{Globe}{12}{\href{https://www.github.com/aarrico}{github.com/aarrico}}\\
		\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/aarrico}{linkedin.com/in/aarrico}}\\
	\end{minipage}

	\vspace{0.5cm}

	%----------------------------------------------------------------------------------------
	%	INTRODUCTION & SKILLS
	%----------------------------------------------------------------------------------------

	\cvsect{Summary}

	\begin{minipage}[t]{0.4\textwidth} % Left column with the introduction text, change the width as needed
		\vspace{-\baselineskip} % Required for vertically aligning minipages
		Hands-on engineering leader with over nine years of experience building and mentoring high-performing teams to deliver scalable, customer-centric software solutions. Proven success in architecting and developing robust applications with Node.js. React, and AWS, including a high-volume messaging service leveraging AWS Lambda that handles over 350,000 daily messages.
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.5\textwidth} % Right column with the skills bar chart, change the width as needed
			% Required for vertically aligning minipages
			\vspace{-\baselineskip} % Required for vertically aligning minipages
			\vspace{-\baselineskip} % Required for vertically aligning minipages
			\vspace{-\baselineskip} % Required for vertically aligning minipages
			\vspace{-\baselineskip}
		\cvsect{Technical Proficiencies}
		
		\textbf{Backend:} Node.js, Python, Java, Go, Express.js, Flask, PostgreSQL, MongoDB, DynamoDB \\
		
		\textbf{Frontend Mobile:} React, JavaScript, TypeScript, HTML/CSS, Flutter \\
		
		\textbf{Cloud DevOps:} AWS (EC2, Lambda, SQS), GCP, Docker, CI/CD, Terraform, GitHub Actions, DataDog \\
		
		\textbf{APIs Testing:} RESTful API Development, OpenAPI, Unit Testing, AAT, Postman \\
		
		\textbf{Methodologies:} Agile/Scrum, Performance Optimization, Cloud Architecture, Technical Documentation \\
		
	\end{minipage}

	\vspace{0.5cm}

	%----------------------------------------------------------------------------------------
	%	ACCOMPLISHMENTS SECTION
	%----------------------------------------------------------------------------------------

	\cvsect{ACCOMPLISHMENTS}
	\begin{itemize}
        
		\item[-] Led a cross-functional team of 5 (engineers, QA, and product) while contributing as an individual developer to rebuild a communication platform for hourly workers and their managers using Node.JS/React.JS, migrating 20,000 users to the new platform in under a year from a Java (Spring Boot) backend and no-code frontend.
	    
		\item[-] Architected and developed the backend for a high-volume messaging service using Twilio and AWS (Lambdas, SQS) that processed over 350,000 outbound and 12,000 inbound messages daily, achieving near real-time interactions between hourly workers and managers.
	    
		\item[-] Developed and implemented a Python scripting API within a Java desktop application, enabling customers to automate workflows and significantly reducing user in-app time by a factor of 30.
	    
		\item[-] Founded Optricity Corp's first engineering team, establishing standard operating procedures based on Agile principles, resulting in a 65% increase in ticket completion rates and instilling a growth mindset in the junior engineers so we could always be building the best thing possible for the organization.
	    
    \end{itemize}

	%----------------------------------------------------------------------------------------
	%	EXPERIENCE
	%----------------------------------------------------------------------------------------

	\cvsect{Experience}

	\begin{entrylist}
        
		\entry
		{05.2022-11.2023}
		{Engineering Manager}
		{Hourwork, Inc.}
        {Spearheaded the complete overhaul of the flagship product, managing a team of three engineers and transitioning over 20,000 users to the new platform in 11 months.\Re-architected the product's Node.js backend and data models, optimizing performance by reducing average database query times by a factor of 200.\Revolutionized the development workflow by implementing robust engineering processes, enabling weekly feature releases.\Provided regular performance reviews and mentored team members.}
        
		\entry
		{06.2021-04.2022}
		{Lead Software Engineer}
		{BlueMark}
        {Developed a RESTful API for an e-commerce platform using Python/Flask and PostgreSQL on AWS EC2.\Reduced bugs in QA by 70% by implementing a robust unit testing and automated acceptance testing (AAT) framework with pytest and Jest.}
        
		\entry
		{01.2019 - 01.2021}
		{Director of Technology}
		{Optricity Corp.}
        {Grew the development team from one to four members, establishing all hiring and onboarding processes.\Reduced load times for large projects by 70% by re-architecting the flagship product's project loading process.\Integrated a Python scripting API within the Java product, resulting in a 60% reduction in customer-reported bugs.}
        
		\entry
		{01.2016 - 01.2019}
		{Software Engineer}
		{Optricity Corp.}
        {Developed a quality control scanner authored in Python/Flask and React to review client data files for any errors, reducing the client success team's help desk tickets by 20%.\Developed a web services API for the Java flagship product, enabling customers to connect their Warehouse Management System directly to the program and eliminating manual file uploads.}
        
    \end{entrylist}

	%----------------------------------------------------------------------------------------
	%	EDUCATION
	%----------------------------------------------------------------------------------------

	\cvsect{Education}

	\begin{entrylist}
		\entry
        
		\entry
		{2012-2014}
		{Master of Science in Materials Science & Engineering}
		{University of Tennessee}
        {Knoxville, TN}
        
		\entry
		{2008-2012}
		{BS in Physics, BA in Computer Science, BA in Mathematics}
		{Duquesne University}
        {Pittsburgh, PA}
        
	\end{entrylist}

	%----------------------------------------------------------------------------------------
	%	PROJECTS
	%----------------------------------------------------------------------------------------

	\cvsect{Personal Projects}
	\begin{entrylist}
        
		\entry
		{Mobile App}
		{Macro Calculator}
		{\texttt{Flutter}}
        {Developing a mobile application in Flutter to calculate food quantities required to meet specific macronutrient goals for meal planning.}
        
		\entry
		{Mobile App}
		{Personal Trainer Study Helper}
		{\texttt{React Native}}
        {Built a mobile study aid using React Native to prepare for personal trainer certification, featuring flashcards and quizzes to reinforce learning.}
        
	\end{entrylist}

	%----------------------------------------------------------------------------------------

	\cvsect{Hobbies}
	\begin{itemize}[leftmargin=*]
    
	\item[]Pokémon Master
    
	\item[]Bodybuilding
    
	\item[]Expert Cinnamon Roll Baker
    
	\item[]Pug Dad
    
	\end{itemize}

\end{document}